Effects

### 2020-01-02 doc/Effects.Rmd
changed plot to better see spread of points

mm <- mouse.table.mean.MLH1.obs_qual[mouse.table.mean.MLH1.obs_qual$sex == "male",]
age.effect.plot.mm <- ggplot(mm, aes(y=mean.MLH1, x=quality, color=(strain) ))+geom_point()+ 
  scale_color_manual(values=colors_of_strains)+ #this list in setupdata
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+ggtitle("Male quality and mean CO")+facet_wrap(~subsp)+
  theme(legend.position="none")

@@

age.effect.plot.ff <- ggplot(ff, aes(y=mean.MLH1, x=quality, color=(strain) ))+geom_point()+ 
  scale_color_manual(values=colors_of_strains)+ #this list in setupdata
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+
  #are the lines
  ggtitle("Female quality and mean CO")+facet_wrap(~subsp)+theme(legend.position="none")

>>>>

mm <- mouse.table.mean.MLH1.obs_qual[mouse.table.mean.MLH1.obs_qual$sex == "male",]
age.effect.plot.mm <- ggplot(mm, aes(y=mean.MLH1, x=quality, color=(strain) ))+geom_jitter(width = 0.16)+ 
  scale_color_manual(values=colors_of_strains)+ #this list in setupdata
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+ggtitle("Male quality and mean CO")+facet_wrap(~subsp)+
  theme(legend.position="none")

@@

age.effect.plot.ff <- ggplot(ff, aes(y=mean.MLH1, x=quality, color=(strain) ))+geom_jitter(width = 0.16)+ 
  scale_color_manual(values=colors_of_strains)+ #this list in setupdata
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+
  #are the lines
  ggtitle("Female quality and mean CO")+facet_wrap(~subsp)+theme(legend.position="none")
